An Efficient Calculus for Generalised Parikh Images of Regular Languages

### 2022-07-05 main.tex
More text

%% Title information
\title{An Efficient Calculus for Generalised Parikh Images of Regular Languages}
                                        %% when present, will be used in
                                        %% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

@@

The Parikh map is a characterisation of a context-free language as a vector of
its character counts, famously a semilinear set~\cite{parikh-theorem}. It
appears naturally as part of many operations in model checking and the solving
of string constraints in automata-based string solvers such as \Ostrich{},
notably in representing constraints on string lengths.

@@

In addition to the elimination of existentially quantified variables, another
problem arises for the common case of solving length constraints in string
solvers. Conjunctions of string constraints lead to the computation of Parikh
images of products (intersections) of regular languages represented as finite
automata. Applying the approach in~\cite{generate-parikh-image} would require
the eager computation of the product before its Parikh image. In several
instances we have observed while solving real-world string constraints, the
computation of the product of automata exhausts the memory of any machine
available due to the exponential blow-up in size of the product, quickly
becoming intractable as the number of automata in the product increases.

Addressing these concerns, we have developed a calculus for Parikh images of
products of regular languages that we call \Calculus{}. It allows us to
interleave the computation of arbitrarily deep products of automata with the
product's Parikh image, and is generalised to an arbitrary Parikh-like
homomorphism over automata labels. This enables us to let both calculations
inform each other, eliminating unnecessary work, and pruning the size of the
partial products considered in the computation for a smaller memory footprint.
Moreover, the method can be used iteratively to tackle smaller chunks of the
product incrementally, thereby avoiding running out of memory at all. We
implement this calculus, along with the approximate method
of~\cite{approximate-parikh}, its fall-back variant adapted
from~\cite{generate-parikh-image}, and an adapter for the \Nuxmv{} model
checker, in a tool that we call \Catra{}. \Catra{} allows solving constraints
over groups of synchronised (products of) Parikh automata, that is
(finite-alphabet) symbolic automata with transitions that increment and
decrement integer registers and that allows checking linear constraints on these
registers after running the automata. Parikh automata without constraints on the
final values on their registers are also sometimes called cost-enriched
automata, weighted automata or counter automata, depending on your definitions
and side-constraints. In the satisfaction mode, we are more formally solving the
intersection problem of Parikh automata (under homomorphism), known to be
PSPACE-complete~\cite{graph-queries}.

Additionally, \Catra{} is able to efficiently generate a quantifier-free
Presburger formula representing such an instance of constraints and automata,
something beyond the reach of general model checkers like~\Nuxmv.

@@

To illustrate the key features of our approach, we start with two regular
languages, a commutative homomorphism $f$ on them that we care about, and a side
constraint for which we want to find values in $f$'s image over the intersection
of the two languages. We will use the same two regular languages,
$\mathtt{ac^*a|b(bb)^*c}$ and $\mathtt{.^*c.^*}$ for both examples but change
the constraint $\varphi$ and homomorphism $f$. In essence, we solve the
following set of constraints for all possible values of $s$ and
$\MonoidElement$:

@@

\begin{figure}[h]
  \begin{minipage}[b]{0.75\linewidth}
  \centering 
    \includegraphics[width=\textwidth]{aca_or_bc}
    \caption{An automaton recognising the regular expression
    $\mathtt{ac^*a|b(bb)^*c}$.}\label{fig:aca-or-bc}

@@

The na\"ive approach would be to first compute the product of the automata, then
use the standard approach to find its image under $f$, and then verify the
constraints. However, we can take advantage of the both constraints and
definitions of $f$ to prune the automata before computing the product and help
reduce the blow-up. To give an intuition for the core idea of \Calculus{}, we
will annotate the transitions of $\SomethingCSomething$ and $\AcaOrBc$ with
variables illustrating how many times they are taken, and perform informal
reasoning on them corresponding to the reasoning performed by our calculus.

\begin{figure}[h]
  \centering 
    \includegraphics[width=0.75\linewidth]{aca_or_bc_simplified}
    \caption{$\AcaOrBc{}$ with its symbolic transition counters after
    simplification of their equations.}\label{fig:example-simplify-1}
  \end{figure}

Note that we have already performed some reasoning in the starting figures -- we
use the same symbol for the number of times each of the upper transitions of
$\AcaOrBc$ are taken, since we know that they must be taken the same number of
times, and we introduced the constant $1$ for the middle transition in
$\SomethingCSomething$, since it must always be taken precisely once to reach
the accepting state. We use standard graph-theoretical flow reasoning to set the
initial flow into the starting state to 1 and use linear equations to enforce
balanced flow throughout the automaton to determine the relations between the
counting variables on each transition (e.g. $1 + {l_b}' = l_a + l_b$, or $l_a +
l_c' = 1$). Strictly speaking, this is where the constant number $1$ in
\cref{fig:something-c-something} comes: from $1 + r_\Sigma = x + r_\Sigma$
solved for $x$. Using analogous linear equation reasoning loses additional
variables and gives us the annotations in \cref{fig:example-simplify-1}.

@@

\begin{figure}[h]
  \centering 
    \includegraphics[width=0.75\linewidth]{something_c_something_length_simplified}
    \caption{$\SomethingCSomething{}$ after using linear reasoning over lengths to replace a variable.}\label{fig:example-length-reduced}
  \end{figure}

@@

\begin{figure}[h]
  \centering 
    \includegraphics[width=0.75\linewidth]{aca_or_bc_length_split_1}
    \caption{$\AcaOrBc{}$ at the split where $\FromLabelTo{start}{a}{sawA}$ is not used.}\label{fig:aca-or-bc-length-split-1}
  \end{figure}

@@

  \begin{figure}[h]
    \centering 
      \includegraphics[width=0.75\linewidth]{aca_or_bc_length_split_2}
      \caption{$\AcaOrBc{}$ at the split where $\FromLabelTo{start}{a}{sawA}$ is used.}\label{fig:aca-or-bc-length-split-2}
    \end{figure}

@@

\begin{figure}[h]
  \centering 
    \includegraphics[width=0.75\linewidth]{length_split_product}
    \caption{The product of $\AcaOrBc$ and $\SomethingCSomething$ after
    case splitting and removal of dead states.}\label{fig:length-split-product}
  \end{figure}

@@

\begin{figure}[h]
  \centering 
    \includegraphics[width=0.75\linewidth]{aca_or_bc_simplified_2}
    \caption{$\AcaOrBc{}$ after removing the now unused b-transition.}\label{fig:example-simplify-2}
  \end{figure}

@@

  \begin{figure}[h]
    \centering 
      \includegraphics[width=0.75\linewidth]{aca_or_bc_simplified_3}
      \caption{$\AcaOrBc{}$ after further constraint propagation.}\label{fig:example-simplify-3}
    \end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=0.75\linewidth]{aca_or_bc_times_something_c_something}
    \caption{$\AcaOrBc{} \times \SomethingCSomething{}$ under the constraint
    $\TransitionCount{a} > \TransitionCount{b}$. Note the fresh variables
    introduced for the transitions (for most transitions the same one, since
    they are all linearly dependent).}\label{fig:final-example}
  \end{figure}

  \begin{figure}[h]
\centering
    \includegraphics[width=0.75\linewidth]{original_product}
    \caption{$\AcaOrBc{} \times \SomethingCSomething{}$ as it would have
    appeared if we had computed it from the initial
    automata.}\label{fig:original-product}
  \end{figure}

@@

\contents{
  \item Formally analyse the complexity of how much easier the length problem is
}

@@

\section{Implementation and Experiments}\label{sec:implementation}

@@

\Catra{} is written in Scala, with the calculus described in this paper
implemented as a theory plug-in for the \Princess{} automated theorem
prover~\cite{princess}, which also performs the Presburger reasoning. For
comparison, we also provide an implementation of the baseline method
from~\cite{generate-parikh-image}, a direct translation that uses the~\Nuxmv{}
symbolic model checker~\cite{nuxmv} to solve our constraints, and \Fudge{the
approximation described in~\cite{approximate-parikh} on top of the standard
baseline back-end}. An example of an input file \Fudge{illustrating every feature
of the file format} can be seen in \cref{lst:input-example}.

@@

\begin{algorithm}
  \caption{An algorithm with caption}\label{alg:baseline}
  \KwData{$\Automaton_1, \ldots, \Automaton_n$ automata, other constraints $\SomeClause$}
  \KwResult{\textsc{Sat} or \textsc{Unsat}}
  \SetKwFunction{NewTheoremProver}{newTheoremProver}
  \SetKwFunction{NewPriorityQueue}{newPriorityQueue}
  \SetKwFunction{Dequeue}{dequeue}
  \SetKwFunction{Enqueue}{enqueue}
  \SetKwFunction{Assert}{assert}

@@

\subsection{\Catra{} is Versatile: Encoding Epistemic Logic Problems As Parikh Automata}

\contents{
\item Model-checking examples e.g. \cite{epistemic-logic}
}

\subsection{\Catra{} is Faster Than The Competition: Benchmarks and Their Results}\label{sec:experiments}

@@

\subsubsection{Execution Time and Ability to Solve Instances}\label{sec:runtime}

@@

\begin{figure}
  \includegraphics[width=0.75\linewidth]{graphs/\commit-by-solver.pdf}
  \caption{The division of statuses per backend.}
  \label{fig:solve-division}
\end{figure}

\begin{figure}
  \includegraphics[width=0.75\linewidth]{graphs/\commit-time-boxplot.pdf}
  \caption{The distribution of runtimes for solved instances per backend. Note that the number of instances solved differs between backends.}
  \label{fig:runtime-boxplot}
\end{figure}

\begin{figure}
  \begin{minipage}[b]{0.75\linewidth}
    \centering 
      \includegraphics[width=\textwidth]{graphs/\commit-duels-lazy-baseline-scatter}
      \caption{Runtime duel: \Calculus{} versus baseline.}
      \includegraphics[width=\textwidth]{graphs/\commit-duels-lazy-nuxmv-scatter}
      \caption{Runtime duel: \Calculus{} versus \Nuxmv.}
    \end{minipage}  
  \caption{The pairwise runtime of each instance for instances solved by any backend. Timeouts are reported as a runtime of \RuntimeTimeout.}
  \label{fig:duels}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.75\linewidth]{graphs/\commit-cactus.pdf}
  \caption{The number of instances solved as the time budget increases, simulated from one \RuntimeTimeout-timeout run.}
  \label{fig:cactus}
\end{figure}

\subsubsection{Finding a Presburger Formula}\label{sec:evaluation:finding-image}

For baseline and \Calculus{}, \Catra{} offers the ability to find the equivalent Presburger formula representing a given instance. For baseline, we use the built-in quantifier elimination facilities of the underlying \Princess{} theorem prover, while for \Catra{} \Fudge{we use the specially tailored approach described in some section}. For this experiment, we use only the~\NrKnownSat{} instances known to be satisfiable from the previous experiment detailed in Sections~\ref{sec:scaling} and~\ref{sec:runtime}.

To make sure baseline puts up as much competition as possible, we disable
checking intermittent satisfiability and configure \Catra{} to run in the
maximally eager mode where the product is first computed before any
satisifiability check is performed. We run the experiments with a timeout of~\ImageTimeout{}. The results of the experiment is summarised
in Figure~\ref{fig:cactus:image} and Table~\ref{tab:image-results}. \Fudge{We see here that something happens}.

\begin{figure}
  \caption{The number of instances \Catra{} was able to find the Presburger form of the image for within a given number of seconds per backend.}
  \label{fig:cactus:image}
\end{figure}

@@

\section{Conclusions}

@@

\section{Discussions}

\contents{
\item cf Parikh Images of Grammars: Complexity and Applications -- what is the best complexity we can do? https://ieeexplore.ieee.org/abstract/document/5571050

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This material is based upon work supported by the
  \grantsponsor{GS100000001}{National Science
    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
  No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the author and do not necessarily reflect the views of the
  National Science Foundation.
\end{acks}

>>>>

%% Title information
\title{An Efficient Calculus for Generalised Parikh Images of Regular Languages}
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

@@

The Parikh map is a characterisation of a context-free language as a vector of
its character counts, famously a semilinear set~\cite{parikh-theorem}. It
appears naturally as part of \Fudge{many operations} in model checking and
solving string constraints in automata-based solvers such as \Ostrich{}
\cite{ostrich}, notably in representing constraints on string lengths.
Specialised string solvers like e.g. Trau \cite{trau} also perform extensive
reasoning using Parikh images, but do so on restricted automata that do not
suffer from the blow-up we seek to address, though it might be possible to
adapts aspects of our approach to theirs.

@@

In addition to the elimination of existentially quantified variables, another
problem arises from length constraints in string solvers. Conjunctions of string
constraints lead to the computation of length images of products (intersections)
of regular languages represented as finite automata. Applying the approach
in~\cite{generate-parikh-image} would require the eager computation of the
product before its length image. In several instances we have observed while
solving real-world string constraints, the computation of the product of
automata exhausts the memory of any machine available due to the exponential
blow-up in size of the product, quickly becoming intractable as the number of
automata in the product increases. The current best published mitigation for
this problem is an over-approximation that works by approximating the Parikh
image of a product of automata to be the conjunction of the image of the
individual automata of the product \cite{approximate-parikh}. This approach only
works for unsatisfiable instances, and comes with a harsh penalty on satisfiable
instances.

Addressing these concerns, we have developed a calculus for Parikh images of
products of regular languages that we call \Calculus{}. It allows us to
interleave the computation of arbitrarily deep products of automata with the
product's Parikh image, and is generalised to an arbitrary Parikh-like
homomorphism over automata labels, including string lengths. This enables us to
let both calculations inform each other, eliminating unnecessary work, and
pruning the size of the partial products considered in the computation for a
smaller memory footprint. Moreover, the method can be used iteratively to tackle
smaller chunks of the product incrementally, thereby avoiding running out of
memory at all.

The problem of computing constraints on Parikh images over products of regular
languages under a given commutative homomorphism amounts to solving products of
Parikh automata. Parikh automata are regular automata extended with integer
counters with given increments and decrements for each transition, where we
allow checking a set of linear constraints on the final values of the counters
(but not their intermittent values) \cite{parikh-automata}. Parikh automata
without constraints on the final values on their registers are also sometimes
called cost-enriched automata, weighted automata or counter automata, depending
on exact definitions and side-constraints. The decision problem tackled in this
paper, determining the emptiness of an intersection of Parikh automata, was
recently shown to be PSPACE-complete~\cite{graph-queries}.

In addition to the decision problem of determining whether an intersection of
Parikh automata is empty and the satisfaction problem of finding a value from
the intersection if it is not, \Catra{} is able to efficiently generate a
quantifier-free Presburger formula representing an intersection of Parikh
automata, something beyond the reach of general model checkers like~\Nuxmv.
\Fudge{This is useful because the moon is made of cheese.}

We implement \Calculus{} as a theory for the \Princess{} automated theorem
prover in a tool that we call \Catra{}. \Catra also supports using the
approximate method of \cite{approximate-parikh}, its fall-back variant adapted
from~\cite{generate-parikh-image}, and an adapter for the \Nuxmv{} model
checker~\cite{nuxmv}. Using \Catra{}, we compare \Calculus{} to the other two
back-ends on \NrBenchmarks{} Parikh automata satisfaction problems generated
\Fudge{by Ostrich+}.

@@

To illustrate the key features of \Calculus, we start with two regular
languages, a commutative homomorphism $f$ on them that we care about, and a side
constraint for which we want to find values in $f$'s image over the intersection
of the two languages using a heavily elided version of \Calculus. We will use
the same two regular languages, $\mathtt{ac^*a|b(bb)^*c}$ and $\mathtt{.^*c.^*}$
for both examples but change the constraint $\varphi$ and homomorphism $f$. In
essence, we solve the following set of constraints for all possible values of
$s$ and $\MonoidElement$:

@@

\begin{figure}[ht]
  \begin{minipage}[b]{0.75\linewidth}
  \centering 
    \includegraphics[width=\textwidth]{aca_or_bc}
    \caption{An automaton recognising the regular expression
    $\mathtt{ac^*a|b(bb)^*c}$.}\label{fig:aca-or-bc}

@@

The na\"ive approach would be to first compute the product of the automata, then
use the approach from \cite{generate-parikh-image} to find its image under $f$,
and then verify the constraints. However, we can take advantage of both the
constraints and definitions of $f$ to prune the automata before computing the
product and help reduce the blow-up.

To give an intuition for the core idea of \Calculus{}, we will annotate the
transitions of $\SomethingCSomething$ and $\AcaOrBc$ with variables illustrating
how many times they are taken, and perform informal reasoning on them
corresponding to the reasoning performed by our calculus.

\begin{figure}[ht]
  \centering 
    \includegraphics[width=0.75\linewidth]{aca_or_bc_simplified}
    \caption{$\AcaOrBc{}$ with its symbolic transition counters after
    simplification of their equations.}\label{fig:example-simplify-1}
  \end{figure}

Note that we have already performed some reasoning in the starting figures; we
use the same symbol for the number of times each of the upper transitions of
$\AcaOrBc$ are taken, since we know that they must be taken the same number of
times, and we introduced the constant $1$ for the middle transition in
$\SomethingCSomething$, since it must always be taken precisely once to reach
the accepting state. We use standard graph-theoretical flow reasoning to set the
initial flow into the starting state to 1 and use linear equations to enforce
balanced flow throughout the automaton to determine the relations between the
counting variables on each transition (e.g. $1 + {l_b}' = l_a + l_b$, or $l_a +
l_c' = 1$). Strictly speaking, this is where the constant number $1$ in
\cref{fig:something-c-something} comes: from $1 + r_\Sigma = x + r_\Sigma$
solved for $x$. Using analogous linear equation reasoning loses additional
variables and gives us the annotations in \cref{fig:example-simplify-1}.

@@

\begin{figure}[ht]
  \centering 
    \includegraphics[width=0.75\linewidth]{something_c_something_length_simplified}
    \caption{$\SomethingCSomething{}$ after using linear reasoning over lengths to replace a variable.}\label{fig:example-length-reduced}
  \end{figure}

@@

\begin{figure}[ht]
  \centering 
    \includegraphics[width=0.75\linewidth]{aca_or_bc_length_split_1}
    \caption{$\AcaOrBc{}$ at the split where $\FromLabelTo{start}{a}{sawA}$ is not used.}\label{fig:aca-or-bc-length-split-1}
  \end{figure}

@@

  \begin{figure}[ht]
    \centering 
      \includegraphics[width=0.75\linewidth]{aca_or_bc_length_split_2}
      \caption{$\AcaOrBc{}$ at the split where $\FromLabelTo{start}{a}{sawA}$ is used.}\label{fig:aca-or-bc-length-split-2}
    \end{figure}

@@

\begin{figure}[ht]
  \centering 
    \includegraphics[width=0.75\linewidth]{length_split_product}
    \caption{The product of $\AcaOrBc$ and $\SomethingCSomething$ after
    case splitting and removal of dead states.}\label{fig:length-split-product}
  \end{figure}

@@

\begin{figure}[ht]
  \centering 
    \includegraphics[width=0.75\linewidth]{aca_or_bc_simplified_2}
    \caption{$\AcaOrBc{}$ after removing the now unused b-transition.}\label{fig:example-simplify-2}
  \end{figure}

@@

  \begin{figure}[ht]
    \centering 
      \includegraphics[width=0.75\linewidth]{aca_or_bc_simplified_3}
      \caption{$\AcaOrBc{}$ after further constraint propagation.}\label{fig:example-simplify-3}
    \end{figure}

@@

\begin{figure}[ht]
\centering
    \includegraphics[width=0.75\linewidth]{aca_or_bc_times_something_c_something}
    \caption{$\AcaOrBc{} \times \SomethingCSomething{}$ under the constraint
    $\TransitionCount{a} > \TransitionCount{b}$. Note the fresh variables
    introduced for the transitions (for most transitions the same one, since
    they are all linearly dependent).}\label{fig:final-example}
  \end{figure}

  \begin{figure}[ht]
\centering
    \includegraphics[width=0.75\linewidth]{original_product}
    \caption{$\AcaOrBc{} \times \SomethingCSomething{}$ as it would have
    appeared if we had computed it from the initial
    automata.}\label{fig:original-product}
  \end{figure}

@@

@@

\section{Implementation}\label{sec:implementation}

@@

\Catra{} is written in Scala, with the calculus described in this paper
implemented as a theory plug-in for the \Princess{} automated theorem
prover~\cite{princess}, which also performs the Presburger reasoning. For
comparison, we also provide an implementation of the baseline method
from~\cite{generate-parikh-image}, a direct translation that uses the~\Nuxmv{}
symbolic model checker~\cite{nuxmv} to solve our constraints, and the
approximation described in~\cite{approximate-parikh} on top of the standard
baseline back-end. An example of an input file corresponding to our running
example introduced in \cref{sec:motivation} can be seen in
\cref{lst:input-example}.

@@

\begin{algorithm}
  \caption{How we implement the baseline approach}\label{alg:baseline}
  \KwData{$\Automaton_1, \ldots, \Automaton_n$ automata, other constraints $\SomeClause$}
  \KwResult{\textsc{Sat} or \textsc{Unsat}}
  \SetKwFunction{NewTheoremProver}{newTheoremProver}
  \SetKwFunction{NewPriorityQueue}{newPriorityQueue}
  \SetKwFunction{Dequeue}{dequeue}
  \SetKwFunction{Enqueue}{enqueue}
  \SetKwFunction{Assert}{assert}

@@

\section{Evaluation}\label{sec:experiments}

@@

\subsection{Execution Time and Ability to Solve Instances}\label{sec:runtime}

@@

\begin{figure}[ht]
  \includegraphics[width=0.75\linewidth]{graphs/\commit-by-solver.pdf}
  \caption{The division of statuses per backend.}
  \label{fig:solve-division}
\end{figure}

\begin{figure}[ht]
  \includegraphics[width=0.75\linewidth]{graphs/\commit-time-boxplot.pdf}
  \caption{The distribution of runtimes for solved instances per backend. Note that the number of instances solved differs between backends.}
  \label{fig:runtime-boxplot}
\end{figure}

\begin{figure}[ht]
  \begin{minipage}[b]{0.75\linewidth}
    \centering 
      \includegraphics[width=\textwidth]{graphs/\commit-duels-lazy-baseline-scatter}
      \caption{Runtime duel: \Calculus{} versus baseline.}
      \includegraphics[width=\textwidth]{graphs/\commit-duels-lazy-nuxmv-scatter}
      \caption{Runtime duel: \Calculus{} versus \Nuxmv.}
    \end{minipage}  
  \caption{The pairwise runtime of each instance for instances solved by any backend. Timeouts are reported as a runtime of \RuntimeTimeout.}
  \label{fig:duels}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[width=0.75\linewidth]{graphs/\commit-cactus.pdf}
  \caption{The number of instances solved as the time budget increases, simulated from one \RuntimeTimeout-timeout run.}
  \label{fig:cactus}
\end{figure}

\subsection{Finding a Presburger Formula}\label{sec:evaluation:finding-image}

For baseline and \Calculus{}, \Catra{} offers the ability to find the equivalent Presburger formula representing a given instance. For baseline, we use the built-in quantifier elimination facilities of the underlying \Princess{} theorem prover, while for \Catra{} we use the specially tailored approach described in \cref{sec:finding-the-image}. For this experiment, we use only the~\NrKnownSat{} instances known to be satisfiable from the previous experiment detailed in \cref{sec:scaling,sec:runtime}.

To make sure baseline puts up as much competition as possible, we disable
checking intermittent satisfiability and configure \Catra{} to run in the
maximally eager mode where the product is first computed before any
satisifiability check is performed. We run the experiments with a timeout
of~\ImageTimeout{}. The results of the experiment is summarised in
\cref{fig:cactus:image} and \cref{tab:image-results}. \Fudge{We see here that
something happens}.

\begin{figure}[ht]
  \caption{The number of instances \Catra{} was able to find the Presburger form of the image for within a given number of seconds per backend.}
  \label{fig:cactus:image}
\end{figure}

@@

\section{Conclusion}

@@

%% Acknowledgments
% \begin{acks}                            %% acks environment is optional
%                                         %% contents suppressed with 'anonymous'
%   %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
%   %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
%   %% acknowledge financial support and will be used by metadata
%   %% extraction tools.
%   This material is based upon work supported by the
%   \grantsponsor{GS100000001}{National Science
%     Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
%   No.~\grantnum{GS100000001}{nnnnnnn} and Grant
%   No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
%   conclusions or recommendations expressed in this material are those
%   of the author and do not necessarily reflect the views of the
%   National Science Foundation.
% \end{acks}
